Multitask matrix completion for learning protein interactions across diseases

### 2016-08-22 paper.tex
some updates

\begin{figure*}
\begin{floatrow}
\ffigbox[0.29\textwidth]{%
%trim option's parameter order: left bottom right top
\includegraphics[scale=0.33, trim = 0.2 9.2cm 4cm 0]{fig1.eps}
}
{
\caption{Multiple bipartite graphs: on the left are host proteins and on the right are proteins from different virus species. Edges represent protein interactions.}
\label{fig:hpppigraph}
}
\capbtabbox[0.69\textwidth]{%
\begin{footnotesize}
\begin{tabular}{crrr} \toprule
Task $\rightarrow$ & \textbf{\textit{Influenza A}} & \textbf{\textit{Hepatitis C}} & \textbf{\textit{Ebola}}\\ \midrule 
number of HP PPIs (positives) & 848& 981 & 90 \\\hline
\# of distinct virus proteins in PPIs & 54 & 151 & 2 \\\hline
{\# of distinct human proteins in PPIs} & 362 & 385 & 88 \\\hline
{total \# of virus proteins across strains} & 542 & 163 & 150 \\\hline
{number of negatives} & 84800 & 98100 & 9000 \\\hline
{density of observed graph$^\ddagger$ (as \%)} & .15 & .60 & .06 \\\hline
\multicolumn{4}{l}{\scriptsize{HP PPI: host-pathogen protein protein interactions}}\\
\multicolumn{4}{l}{\scriptsize{$\ddagger$: considering all proteins in the two organisms involved. }}\\
\multicolumn{4}{l}{\scriptsize{Note: considering the total number of human proteins to be $\approx$ 100,000.}}\\
\bottomrule
\end{tabular}
\end{footnotesize}
}
{
\caption{Tasks and their sizes. Each column corresponds to one bipartite graph between human proteins and the pathogen indicated in the column header. All pathogens are single stranded RNA viruses. Row 4 shows that each of our graphs is extremely sparse.} 
\label{datasets}
}
\end{floatrow}
\end{figure*}

@@

The key challenges in inducing such a model are: (1) In addition to the interactions from each graph, it should exploit information available in the form of features. 
(2) Exploiting features is particularly crucial since the graph $\mathcal{G}$ is often extremely sparse, i.e there are a large number of nodes and very few edges are observed. 
There will be proteins (i.e nodes) that are not involved in any known interactions -- called the \textit{cold start problem} in the recommendation systems community. 
The model should be able to predict the existence of links (or their absence) between such prior `unseen' node pairs. 
This is of particular significance in graphs that capture biological phenomena. For instance, the host-pathogen PPI network
of human-Ebola virus (column-3, Table \ref{datasets}) has $\approx$ 90 observed edges (equivalent to 0.06\% of the possible edges) which involve only 2 distinct virus proteins. Any biologist studying virus-human interactions will be interested in knowing more about the hundreds of other virus proteins (which have yet unknown interactions).
(3) A side-effect of having scarce data is the availability of a large number of unlabeled examples, 
i.e pairs of nodes with no edge between them. 
These unlabeled examples can contain information about the graph as a whole, and a good model should be able to use them.
%(4) ---- class skew ----

@@

\subsection{Competing methods}
The results upon comparing our model to various single and multitask methods are shown in Table \ref{resultsTable}. Our baselines include recent low-rank and sparse models, conventional multitask methods and prior work on HP PPI prediction. For a uniform comparison we used least squared loss in all the methods. The MALSAR package was used to implement some of the models. For the baselines wherever appropriate, we concatenated the features of the two node types into a single feature vector. Let $W \in \mathbb{R}^{T \times d_t}$ be the matrix with the task-specific weight vectors $\mathbf{w}_t$.

\noindent\textbf{Single task (STL)}: We used ridge regression with $\ell_2$ regularization (which performed better than $\ell_1$). \\
\noindent\textbf{MMTL}: The mean regularized multitask learning model from \cite{pontil04}. \\
\noindent\textbf{Dirty model} \citep{jalali2010}: This model assumes that $W = P + Q$, where $P$ enforces group sparsity and $Q$ is to control for element-wise sparsity. It uses the regularizer $\rho_1 \|P\|_{1,\infty} + \rho_2 \| Q \|_1$. \\
\noindent\textbf{Low rank model}: A low-rank structure is enforced on $W$ by minimizing the nuclear norm $\|W\|_*$. \\
\noindent\textbf{Sparse + low-rank} \citep{chen2012}: $W$ is assumed to have the decomposition: $W = P + Q$, where $P$ is sparse and $Q$ has a low-rank structure. \\
\noindent\textbf{IMC} \citep{prateek,nagarajan}: This is the link-prediction model from Section \ref{MCintro}, where data from all tasks is combined without incorporating any task relationships. $U$ and $V$ are shared by all tasks. We use the same initialization for this method as we do for our model. A comparison to this model tells us how much we gain from the task-specific sparsity component $S_t$. \\
\noindent\textbf{MTPL} \citep{me_ismb_2013}: A biologically inspired regularizer is used to capture task similarity.\\ \noindent\textbf{BSL-MTL}: Bilinear sparse low-rank multitask learning, the method developed in this paper.

\begin{table*}[t]\caption{Area Under the Precision-Recall curve for each task in the two settings. X\% training indicates the fraction of the labeled data used for training and tuning the model with the rest (100-X)\% used as test data. We report the average AUC-PR over 10 random train-test splits (stratified splits that maintain the class-skew of 1:100). The standard deviation is also shown. The performance of the best baseline and the overall best method (BSL-MTL) is highlighted in bold.}
\label{resultsTable}
\begin{small}
\begin{center}
\def\arraystretch{1.2}
\begin{tabular}{c|ccccccc}
\toprule
& \multicolumn{3}{c}{\textbf{10\% training}} && \multicolumn{3}{c}{\textbf{30\% training}} \\ \cline{2-4}\cline{6-8}
& \textit{Ebola} & \textit{Hep-C} & \textit{Influenza} && \textit{Ebola} & \textit{Hep-C} & \textit{Influenza} \\ \midrule
STL (Ridge Reg.)  & 0.189$\pm$.09 & 0.702$\pm$.08 & 0.286$\pm$.02 && 0.130$\pm$.03 & 0.802$\pm$.03 & 0.428$\pm$.03 \\ 
MMTL \citep{pontil04} & 0.113$\pm$.04 & 0.767$\pm$.03 & 0.321$\pm$.02 && 0.129$\pm$.02 & 0.802$\pm$.04 & 0.430$\pm$.03  \\ 
Trace-norm  & 0.199$\pm$.11 & 0.767$\pm$.03 & 0.318$\pm$.02 && 0.207$\pm$.02 & 0.808$\pm$.02 & 0.409$\pm$.03 \\ 
Sparse+low-rank \citep{chen2012} & 0.144$\pm$.07 & 0.767$\pm$.02 & 0.318$\pm$.02 && 0.153$\pm$.02 & \textbf{0.814}$\pm$.01 & 0.414$\pm$.03  \\ 
Dirty model \citep{jalali2010} & 0.074$\pm$.03 & 0.767$\pm$.04 & 0.324$\pm$.02 && 0.165$\pm$.02 & 0.813$\pm$.03 & 0.412$\pm$.03  \\ 
MTPL \citep{me_ismb_2013} & \textbf{0.217}$\pm$.08 & 0.695$\pm$.02 & 0.345$\pm$.02 && \textbf{0.260}$\pm$.05 & 0.713$\pm$.01 & \textbf{0.496}$\pm$.03 \\ 
IMC \citep{nagarajan} & 0.087$\pm$.04 & \textbf{0.779}$\pm$.02 & \textbf{0.362}$\pm$.01 && 0.122$\pm$.02 & 0.801$\pm$.01 & 0.410$\pm$.03  \\ \midrule
BSL-MTL (this work) & \textbf{0.233}$\pm$.10 & \textbf{0.807}$\pm$.02 & \textbf{0.486}$\pm$.02 && \textbf{0.361}$\pm$.03 & \textbf{0.842}$\pm$.01 & \textbf{0.560}$\pm$.02  \\ \bottomrule
\end{tabular}
\end{center}
\end{small}
\end{table*}

@@

@@

\section{Results}
Table \ref{resultsTable} has the AUC-PR for all methods. 
Note that the AUC-PR of a random classifier model is $\approx 0.01$.
The first row (STL) is the single-task baseline and all others are multitask models. In general, we notice that multitask learning benefits
all tasks. The first three columns show the results in the 10\% setting. 
%The number of training positive examples from each task are 8 for Ebola, 85 for Influenza and 98 for Hepatitis-C. 
Our model (last row) has significant gains for Influenza (1.4 times better than the next best) and modest improvements for the other tasks.
The variance in the performance is high for the Ebola task (column 1) owing to the small number of positives 
in the training splits (8 positives).
The most benefits for our model are seen in the 30\% setting for all tasks, with 
improvements of 39, 3 and 12 percentage points on the \textit{Ebola}, \textit{Hepatitis} and \textit{Influenza} tasks, respectively. \textit{Ebola}, the data-poorest task, benefits the most.

%\noindent\emph{Incorporating further distinct tasks}: We tried including a fourth task, \textit{HIV}-human PPI (which is very distinct from the other three, with \textit{HIV} being a retrovirus). Our model performs

%On the Hepatitis-C task, the single-task learning method is already performing quite well indicating that this task has a lower variance. Hence, the improvement for this task is much lower by all the baselines. Yet the best performance is obtained by our methods.

%Overall, we see great improvements for the two pathogens for which there is less data (Ebola) or less predictive data (Influenza) both over the single-task baseline and over other existing models. Results on the more predictive data (Hepatitis-C) were either as good or had smaller improvements over the baselines. This is consistent with the expectations for multi-task learning, where weakly-performing tasks are lifted more than strongly-performing tasks by borrowing from other related tasks. \\

@@

@@

\begin{figure}
\begin{floatrow}
\ffigbox[0.49\columnwidth]{%
%trim option's parameter order: left bottom right top
\includegraphics[scale=0.25, trim = 0 0.8cm 0 0]{fig2.eps}
\includegraphics[scale=0.23, trim = 0 0 0 0]{fig3.eps}
}{%
\caption{Principal component analysis (PCA) of virus proteins in the original feature space (left) and the projected subspace (right). The first two principal components are shown. Shape of the points indicates which virus that protein comes from.}%
\label{fig:pca}
}
\ffigbox[0.49\columnwidth]{%
%trim option's parameter order: left bottom right top
\includegraphics[scale=0.165, trim = 0 0.8cm 0 0]{fig4.eps}
\includegraphics[scale=0.165, trim = 0 0 0 0]{fig5.eps}
}{%
\caption{Top tri-mer and four-mer sequence motifs from virus proteins across all three viruses. These correspond to features important for interactions.}%
\label{fig:virus_motifs}
}
\end{floatrow}
\end{figure}

@@

\begin{figure}
\begin{floatrow}
\ffigbox[0.23\columnwidth]{%
%trim option's parameter order: left bottom right top
\includegraphics[scale=0.165, trim = 0 0 0 0]{fig6.eps}
}{%
\caption{Sequence motif constructed from the top four-mer features of human proteins}%
\label{fig:human_motifs}
}

\ffigbox[0.23\columnwidth]{%
%trim option's parameter order: left bottom right top
\includegraphics[scale=0.165, trim = 0.2cm 0 0 0]{fig7.eps}
}{%
\caption{Sequence motif from top four-mer features specific to \textit{Ebola} proteins}%
\label{fig:ebola_motifs}
}

@@

\ffigbox[0.23\columnwidth]{%
%trim option's parameter order: left bottom right top
\includegraphics[scale=0.165, trim = 0 0 0 0]{fig8.eps}
}{%
\caption{Sequence motifs specific to \textit{Hepatitic-C} proteins that are also important to interactions.}%
\label{fig:hepc_motifs}
}

\ffigbox[0.23\columnwidth]{%
%trim option's parameter order: left bottom right top
\includegraphics[scale=0.165, trim = 0 0 0 0]{fig9.eps}
}{%
\caption{Sequence motifs specific to \textit{Influenza} proteins that are also important to interactions.}%
\label{fig:flu_motifs}
}
\end{floatrow}
\end{figure}

\section{Conclusions and future extensions}
%Multitask link prediction is an important area with many applications ranging from recommendation systems to biomedical host-pathogen interactions.  
This work developed and tested a new method based on low-rank matrix completion for sharing information across tasks
%and showed significant increases in prediction performance. 
The method was evaluated in the host-pathogen protein interaction domain for three pathogens (three tasks) and exhibited significant increases in prediction accuracy. The model parameters provide several avenues for
studying host-pathogen interactions for biologists that can lead to interesting observations and insights. Finally, the model we present is general enough to be applicable on other problems such as: gene-disease relevance prediction across organisms or disease conditions. 
%As future work we intend to apply our method in some of these other settings.

%We envision many potential extensions to this work, two of which are: \\
%{\em Applications:} We would like to apply our method on a multi-host (e.g. human, mouse, bovine, etc.) multi-pathogen graph to determine if the same multitask learning advantages accrue. Beyond protein interaction graphs, the next step is to apply and evaluate the method for different families of tasks, such recommendation systems data.\\
%{\em Multiple levels:} Task hierarchies can be exploited by our model by incorporating additional components to reflect the hierarchical relationships. 
%{\em Multiple link types:} We investigated one type of link, namely interaction links, but there can be different types of related links, such as between people and scientific articles (e.g. authorship, citation, has-read, dislikes, etc.). It will be interesting to incorporate these into our models.
%  The multiple tasks here are predictions in different but correlated link spaces:  \textit{authorship} + \textit{citation} = \textit{self-citation}, citation is correlated with has-read, citation is anti-correlated with dislikes, but not totally, e.g. if contrasting one's work with a less preferred alternative.

%We feel that multitask learning in link prediction is still in the early stages of research and hope this contribution will stimulate further work.

>>>>

\begin{figure*}
\begin{floatrow}
\ffigbox[0.29\textwidth]{%
%trim option's parameter order: left bottom right top
\includegraphics[scale=0.33, trim = 0.2 9.2cm 4cm 0]{fig1.eps}
}
{
\caption{Multiple bipartite graphs: on the left are host proteins and on the right are proteins from different virus species. Edges represent protein interactions.}
\label{fig:hpppigraph}
}
\capbtabbox[0.69\textwidth]{%
\begin{footnotesize}
\begin{tabular}{c|r|r|r} \toprule
Task $\rightarrow$ &{\textit{Influenza A}} &\textit{Hepatitis C} & {\textit{Ebola}}\\
& (28 strains) & (5 strains,  & (2 strains) \\
& & many isolates) & \\ \midrule 
number of HP PPIs (positives) & 848& 981 & 90 \\\hline
number of non-homologous PPIs & 334 & 329 & 49 \\ \hline
\# of unique virus proteins in dataset & 54 & 151 & 2 \\\hline
\# of unique human proteins in dataset & 362 & 385 & 88 \\\hline
total \# of virus proteins in & 542 & 163 & 38 \\
UniprotKB across strains $^\dagger$ & & & \\ \hline
number of negatives & 84800 & 98100 & 9000 \\\hline
density of observed graph$^\ddagger$ (as \%) & .15 & .60 & .20 \\\hline
\multicolumn{4}{l}{\scriptsize{HP PPI: host-pathogen protein protein interactions}}\\
\multicolumn{4}{l}{\scriptsize{$\ddagger$ Density = (no. of positives + no. of negatives)/ total number of possible edges. The}} \\
\multicolumn{4}{l}{\scriptsize{\hspace{0.1cm} denominator was computed considering all proteins from all strains of the virus and}}\\
\multicolumn{4}{l}{\scriptsize{\hspace{0.1cm} $\approx$ 100,000 human proteins.}}\\
\multicolumn{4}{l}{\scriptsize{$\dagger$ this is the number of `reviewed' proteins on UniprotKB from all strains in our data}} \\
\bottomrule
\end{tabular}
\end{footnotesize}
}
{
\caption{Tasks and their sizes. Each column corresponds to one bipartite graph between human proteins and the pathogen indicated in the column header. All pathogens are single stranded RNA viruses. The last row shows that each of our graphs is extremely sparse.} 
\label{datasets}
}
\end{floatrow}
\end{figure*}

@@

The key challenges in inducing such a model are: (1) In addition to the interactions from each graph, it should exploit information available in the form of features. 
(2) Exploiting features is particularly crucial since the graph $\mathcal{G}$ is often extremely sparse, i.e there are a large number of nodes and very few edges are observed. 
There will be proteins (i.e nodes) that are not involved in any known interactions -- called the \textit{cold start problem} in the recommendation systems community. 
The model should be able to predict the existence of links (or their absence) between such prior `unseen' node pairs. 
This is of particular significance in graphs that capture biological phenomena. For instance, the host-pathogen PPI network
of human-Ebola virus (column-3, Table \ref{datasets}) has $\approx$ 90 observed edges (equivalent to 0.06\% of the possible edges) which involve only 2 distinct virus proteins. 
(3) A side-effect of having scarce data is the availability of a large number of unlabeled examples, 
i.e pairs of nodes with no edge between them. 
These unlabeled examples can contain information about the graph as a whole, and a good model should be able to use them.
%(4) ---- class skew ----

@@

\subsection{Comparison with other machine learning approaches}
\label{mlmethods}
Our baselines include recent low-rank and sparse models, conventional multitask methods and prior work on HP PPI prediction. For a uniform comparison we used least squared loss in all the methods. The MALSAR \cite{malsar} package was used to implement some of the models. For the baselines wherever appropriate, we concatenated the features of the two node types into a single feature vector. Let $W \in \mathbb{R}^{T \times d_t}$ be the matrix with the task-specific weight vectors $\mathbf{w}_t$.

\noindent\textbf{Single task (STL)}: We used ridge regression with $\ell_2$ regularization (which performed better than $\ell_1$). \\
\noindent\textbf{MMTL}: The mean regularized multitask learning model from \cite{pontil04}. \\
\noindent\textbf{Sparse + low-rank} \citep{chen2012}: $W$ is assumed to have the decomposition: $W = P + Q$, where $P$ is sparse and $Q$ has a low-rank structure. \\
\noindent\textbf{IMC} \citep{prateek,nagarajan}: This is the link-prediction model from Section \ref{MCintro}, where data from all tasks is combined without incorporating any task relationships. $U$ and $V$ are shared by all tasks. We use the same initialization for this method as we do for our model. A comparison to this model tells us how much we gain from the task-specific sparsity component $S_t$. \\
\noindent\textbf{MTPL} \citep{me_ismb_2013}: A biologically inspired regularizer is used to capture task similarity.\\ \noindent\textbf{BSL-MTL}: Bilinear sparse low-rank multitask learning, the method developed in this paper.

\subsection{Comparison with a homolog baseline}
In addition to the machine learning methods presented in Section \ref{mlmethods}, we also tried a simple homology based approach that is based on protein sequence identity. We use the entire human-virus interactome from PHISTO as input to this method. Given a human protein $h$, we rank all virus proteins $v$ based on the following simple scheme. let $V(h)$ be a set of all virus proteins interacting with the human protein $h$ and let $H(v)$ be all human proteins interacting with the virus protein $v$. We score each pair $(h, v)$ from the bipartite graph as follows: $\max \{ \max $ sequence identity between $h$ and all host proteins in $H(v)$; $\max $ sequence identity between $ v $ and all virus proteins in $V(h) \}$.

@@

\begin{table*}[t]\caption{Area Under the Precision-Recall curve for each task on the PHISTO dataset without removing the homologs. The column header `X\% training' indicates the fraction of the labeled data used for training and tuning the model with the rest (100-X)\% used as test data. We report the average AUC-PR over 10 random train-test splits (stratified splits that maintain the class-skew of 1:100). The standard deviation is also shown. The performance of the best baseline and the overall best method (BSL-MTL) is highlighted in bold.}
\label{resultsTable}
\begin{small}
\begin{center}
\def\arraystretch{1.2}
\begin{tabular}{c|ccccccc}
\toprule
& \multicolumn{3}{c}{\textbf{10\% training}} && \multicolumn{3}{c}{\textbf{30\% training}} \\ \cline{2-4}\cline{6-8}
& \textit{Ebola} & \textit{Hep-C} & \textit{Influenza} && \textit{Ebola} & \textit{Hep-C} & \textit{Influenza} \\ \midrule
Homolog & & & && & & \\
STL (Ridge Reg.)  & 0.189$\pm$.09 & 0.702$\pm$.08 & 0.286$\pm$.02 && 0.130$\pm$.03 & 0.802$\pm$.03 & 0.428$\pm$.03 \\ 
MMTL \citep{pontil04} & 0.113$\pm$.04 & 0.767$\pm$.03 & 0.321$\pm$.02 && 0.129$\pm$.02 & 0.802$\pm$.04 & 0.430$\pm$.03  \\ 
%Trace-norm  & 0.199$\pm$.11 & 0.767$\pm$.03 & 0.318$\pm$.02 && 0.207$\pm$.02 & 0.808$\pm$.02 & 0.409$\pm$.03 \\ 
Sparse+low-rank \citep{chen2012} & 0.144$\pm$.07 & 0.767$\pm$.02 & 0.318$\pm$.02 && 0.153$\pm$.02 & \textbf{0.814}$\pm$.01 & 0.414$\pm$.03  \\ 
%Dirty model \citep{jalali2010} & 0.074$\pm$.03 & 0.767$\pm$.04 & 0.324$\pm$.02 && 0.165$\pm$.02 & 0.813$\pm$.03 & 0.412$\pm$.03  \\ 
MTPL \citep{me_ismb_2013} & \textbf{0.217}$\pm$.08 & 0.695$\pm$.02 & 0.345$\pm$.02 && \textbf{0.260}$\pm$.05 & 0.713$\pm$.01 & \textbf{0.496}$\pm$.03 \\ 
IMC \citep{nagarajan} & 0.087$\pm$.04 & \textbf{0.779}$\pm$.02 & \textbf{0.362}$\pm$.01 && 0.122$\pm$.02 & 0.801$\pm$.01 & 0.410$\pm$.03  \\ \midrule
BSL-MTL (this work) & \textbf{0.233}$\pm$.10 & \textbf{0.807}$\pm$.02 & \textbf{0.486}$\pm$.02 && \textbf{0.361}$\pm$.03 & \textbf{0.842}$\pm$.01 & \textbf{0.560}$\pm$.02  \\ \bottomrule
\end{tabular}
\end{center}
\end{small}
\end{table*}

@@

\section{Results}
As described in Section \ref{}, the PPI data we obtain from PHISTO has homologs within a task. We therefore present results on two sets of data: (a) with the original PPIs from PHISTO shown in Table \ref{resultsTable} and (b) after removal of all homologs within each task in Table \ref{homresultsTable}. The latter comparison gives us an idea of how much the approaches benefit from the redundancy within each task.

Table \ref{resultsTable} has the AUC-PR for all methods. 
Note that the AUC-PR of a random classifier model is $\approx 0.01$.
The first row (STL) is the single-task baseline and all others are multitask models. In general, we notice that multitask learning benefits
all tasks. The first three columns show the results in the 10\% setting. 
%The number of training positive examples from each task are 8 for Ebola, 85 for Influenza and 98 for Hepatitis-C. 
Our model (last row) has significant gains for Influenza (1.4 times better than the next best) and modest improvements for the other tasks.
The variance in the performance is high for the Ebola task (column 1) owing to the small number of positives 
in the training splits (8 positives).
The most benefits for our model are seen in the 30\% setting for all tasks, with 
improvements of 39, 3 and 12 percentage points on the \textit{Ebola}, \textit{Hepatitis} and \textit{Influenza} tasks, respectively. \textit{Ebola}, the data-poorest task, benefits the most.

\begin{table}[t]\caption{Area Under the Precision-Recall curve for each task upon removal of the homologs within each task, on the 10\% setting}
\label{homresultsTable}
\begin{small}
\begin{center}
\def\arraystretch{1.2}
\begin{tabular}{c|ccc}
\toprule
& \textit{Ebola} & \textit{Hep-C} & \textit{Influenza} \\ \midrule
Homolog & & & \\
STL (Ridge Reg.)  & & & \\
Sparse+low-rank \citep{chen2012} & & &  \\ 
BSL-MTL (this work) & & &  \\ \bottomrule
\end{tabular}
\end{center}
\end{small}
\end{table}

\subsection{Disadvantages of the Homolog method}
In Figures \ref{fig:ebolanet}-\ref{fig:flunet} we show for each task, the protein interactions in the test data (for one train-test split) that were not found by the homologs model which relies purely on homology-based sequence similarity. The interactions mainly involve human proteins which do not have a homolog in the training data. This illustrates that our features capture more information than mere sequence similarity. Further, inclusion of interactions from other viruses in the naive manner as done by the homologs model is not helpful - our model is able to learn what to borrow from the other tasks accurately.

\begin{figure*}
\ffigbox[\textwidth]
{
\begin{subfloatrow}[3]
\ffigbox[0.22\textwidth]{%
%trim option's parameter order: left bottom right top
\includegraphics[scale=0.23, trim = 0.3 0 0.2 0.2]{ebolanet.pdf}\vspace{1cm}
}
{
\caption{Ebola-human PPI}
\label{fig:ebolanet}
}
\ffigbox[0.33\textwidth]{%
%trim option's parameter order: left bottom right top
\includegraphics[scale=0.33, trim = 0.2 0.2 0.2 0.2]{flavinet.pdf}
}
{
\caption{Hepatitis-human PPI}
\label{fig:flavinet}
}
\ffigbox[0.34\textwidth]{%
%trim option's parameter order: left bottom right top
\includegraphics[scale=0.35, trim = 0.2 0.2 0.2 0.2]{flunet.pdf}
}
{
\caption{Influenza-human PPI}
\label{fig:flunet}
}
\end{subfloatrow}
}
{
\caption{PPI from each task that are found by our method but are missed by the homolog method}
}
\end{figure*}

@@

\begin{figure}
\begin{floatrow}
\ffigbox[0.49\columnwidth]{%
%trim option's parameter order: left bottom right top
\includegraphics[scale=0.35, trim = 0 0.8cm 0 0]{fig2.eps}
}{%
\caption{Principal component analysis (PCA) of virus proteins in the original feature space}%
\label{fig:pca1}
}
\ffigbox[0.49\columnwidth]{%
\includegraphics[scale=0.33, trim = 0 0 0 0]{fig3.eps}
}{%
\caption{Principal component analysis (PCA) of virus proteins in the projected subspace. The first two principal components are shown. Shape of the points indicates which virus that protein comes from.}%
\label{fig:pca2}
}
\end{floatrow}
\end{figure}

@@

@@

\begin{figure}
\begin{floatrow}
\ffigbox[0.62\columnwidth]{%
%trim option's parameter order: left bottom right top
\includegraphics[scale=0.165, trim = 0 0.8cm 0 0]{fig4.eps}
\includegraphics[scale=0.165, trim = 0 0 0 0]{fig5.eps}
}{%
\caption{Top tri-mer and four-mer sequence motifs from virus proteins across all three viruses. These correspond to features important for interactions.}%
\label{fig:virus_motifs}
}
\ffigbox[0.31\columnwidth]{%
%trim option's parameter order: left bottom right top
\includegraphics[scale=0.165, trim = 0 0 0 0]{fig6.eps}
}{%
\caption{Sequence motif constructed from the top four-mer features of human proteins}%
\label{fig:human_motifs}
}
\end{floatrow}
\begin{floatrow}
\ffigbox[0.3\columnwidth]{%
%trim option's parameter order: left bottom right top
\includegraphics[scale=0.165, trim = 0.2cm 0 0 0]{fig7.eps}
}{%
\caption{Sequence motif from top four-mer features specific to \textit{Ebola} proteins}%
\label{fig:ebola_motifs}
}

@@

\ffigbox[0.3\columnwidth]{%
%trim option's parameter order: left bottom right top
\includegraphics[scale=0.165, trim = 0 0 0 0]{fig8.eps}
}{%
\caption{Sequence motifs specific to \textit{Hepatitic-C} proteins that are also important to interactions.}%
\label{fig:hepc_motifs}
}

\ffigbox[0.3\columnwidth]{%
%trim option's parameter order: left bottom right top
\includegraphics[scale=0.165, trim = 0 0 0 0]{fig9.eps}
}{%
\caption{Sequence motifs specific to \textit{Influenza} proteins that are also important to interactions.}%
\label{fig:flu_motifs}
}
\end{floatrow}
\end{figure}

\section{Conclusions and future extensions}
%Multitask link prediction is an important area with many applications ranging from recommendation systems to biomedical host-pathogen interactions.  
This work developed and tested a new method based on low-rank matrix completion for sharing information across tasks
%and showed significant increases in prediction performance. 
The method was evaluated in the host-pathogen protein interaction domain for three pathogens (three tasks) and exhibited significant increases in prediction accuracy. The model parameters provide several avenues for
studying host-pathogen interactions for biologists that can lead to interesting observations and insights. Finally, the model we present is general enough to be applicable on other problems such as: gene-disease relevance prediction across organisms or disease conditions.
